{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-06-30 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
continue

\section{Background and Related Work}

@@

While government agencies provide a variety of set of boundaries  
Official urban boundaries are defined by government agencies for political and administrative purposes.

>>>>

\section{Background and Related Work}
In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them.
While government agencies define various sets of boundaries to partition the geographical space into  
However, the spatial extent of these defined unit

Although, their physical boundaries can be adjacent or distant, based on various connections amongst themselves, such as social-economic relations and commute patterns of citizens, certain groups of urban regions are more strongly connected as clusters than others.

how citizens perceive, organize their image of a city and interact with the urban environments. On the other hand, today’s urban boundaries (i.e. edges and districts) are usually defined by government agencies for political and administrative purposes. A fundamental question for this “top-down” based approach to defining urban boundaries is whether it reflects the real situations of humans interacting across space, such as commuting or trading between the borders. Further, the urban boundaries that respect how people naturally interact with the space can be in grate importance for decision makers regarding city planning, resource allocation and even marketing campaigns.

@@

Official urban boundaries are defined by government agencies for political and administrative purposes.
